### 2023-02-12 manuscript.Rmd
Add first draft for rating analysis

@@

```{r tabs1, results="asis"}
# Print table of materials
read_csv(here("materials", "keywords.csv"), col_types = cols()) %>%
  mutate(
    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  ) %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,width=18mm]{materials/unfamiliar_objects/",
      filename,
      "}"
    ),
    item_id = as.character(item_id),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Unfamiliar Object Stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

>>>>

```{r, ratings}
options(rgl.useNULL = TRUE)
load(here(data_dir, "ratings", "dewak100k_lsa.rda"))

rating <- read_csv(
  here(data_dir, "ratings", "rating_data.csv"),
  col_types = cols(), locale = locale(encoding = "latin1")
)

rating_n <- nrow(rating)

rating_substantives <- select(rating, S001_01:S242_01)
rating_verbs <- select(rating, V001_01:V242_01)

keywords <- read_csv(here("materials", "keywords.csv"), col_types = cols()) %>%
  mutate(
    match_ger = str_c(match_noun_ger, ", ", match_verb_ger),
    match_en = str_c("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = str_c(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
    nonmatch_en = str_c("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  )

keywords_for_rating <- keywords %>%
  arrange(familiarity, filename) %>%
  select(item_id, filename, match_ger, nonmatch_ger) %>%
  replicate(rating_n, ., simplify = FALSE) %>%
  bind_rows()

rating_cosine <-
  map2_dfc(rating_substantives, rating_verbs, str_c, sep = ", ") %>%
  mutate(participant_id = rating$CASE) %>%
  pivot_longer(
    cols = -participant_id, names_to = "question_id", values_to = "response"
  ) %>%
  bind_cols(keywords_for_rating, .) %>%
  filter(response != "NA NA") %>%
  rowwise() %>%
  mutate(
    across(c(match_ger, nonmatch_ger, response), str_to_lower),
    cosine_match = LSAfun::costring(match_ger, response, dewak100k_lsa),
    cosine_nonmatch = LSAfun::costring(nonmatch_ger, response, dewak100k_lsa),
    cosine_diff = cosine_match - cosine_nonmatch
  )

write_excel_csv(rating_cosine, here(output_dir, "rating_results.csv"))

# sum(is.na(rating_cosine$cosine_diff))
# t.test(rating_cosine$cosine_diff)

# model_rating <- lmerTest::lmer(diff_cosine ~ 1 + (1 | participant_id), rating_cosine)
```

@@

```{r tabs1, results="asis"}
# Print table of materials
keywords %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,width=18mm]{materials/unfamiliar_objects/",
      filename,
      "}"
    ),
    item_id = as.character(item_id),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Unfamiliar Object Stimuli\\smallskip",
    font_size = "footnotesize"
  )
```
